### 2018-04-10 latex/icpp18/algorithm.tex
finegrain

\paragraph{Randomized checkerboard partitioning(\textbf{CR})}
This scheme corresponds to partitioning both the rows and the columns of $\Am$ into $P_r$ and $P_c$ segments randomly.
It is expected to provide good load and communication balance both in sparse and dense matrix operations, but it overlooks the communication volume.

@@

\paragraph{Fine-grain hypergraph partitioning~(\textbf{FH})}
This is the partitioning strategy employed by \hypertensor.

>>>>

\paragraph{Randomized checkerboard partitioning(\textbf{CRD})}
This scheme corresponds to partitioning both the rows and the columns of $\Am$ into $P_r$ and $P_c$ segments randomly.
It is expected to provide good load and communication balance both in sparse and dense matrix operations, but it overlooks the communication volume.

@@

\paragraph{Fine-grain hypergraph partitioning~(\textbf{FH})}
This is the partitioning strategy employed by \hypertensor.
It forms a fine-grain hypergraph involving a vertex for each nonzero $(\Am(i, j)$ and a hyperedge for each row and column index $i = 1, \dots, m$ and $j = 1, \dots, n$.
The resulting hypergraph is typically very large and is costly to partition, and unlike checkerboard variants fingerprint of processes are not restricted to a row/column stride.
